Technical Paper Proposal: \\ Placement Algorithms for Heterogenous FPGAs

### 2024-09-09 docs/proposal/proposal.tex
prepare references and figures

\documentclass{article}
\usepackage{hyperref}
\usepackage{enumitem}

@@

\section{Abbreviations}
\begin{itemize}[label={--}, left=0.25cm] % Adjust label and left indent as desired
    \item FPGA: Field Programmable Gate Array
    \item VLSI: Very Large Scale Integration
    \item EDA: Electronic Design Automation
    \item VHSIC: Very High Speed Integrated Circuits
    \item HDL: Hardware Description Language
    \item VHDL: VHSIC HDL
    \item HLS: High Level Synthesis
    \item PL-PS: Programmable Logic - Processing System
    \item EDIF: Electronic Design Interchange Format
\end{itemize}

@@

    \item \textbf{Synthesis}
    \begin{itemize}[label={--}, left=0.25cm]
        \item Takes a design written in a high-level HDL like VHDL or Verilog and "synthesizes" a \textbf{logical netlist} out of it. This logical netlist is usually generated as an EDIF, JSON, or a low-level Verilog file. This netlist describes the necessary basic elements of logic (BELs) and the wired connections between them that are necessary to implement the design.
    \end{itemize}

    \item \textbf{Placement}
    \begin{itemize}[label={--}, left=0.25cm]
        \item Takes the \textbf{logical netlist} and produces a \textbf{physical netlist}.
    \end{itemize}

    \item \textbf{Routing}
    \begin{itemize}[label={--}, left=0.25cm]
        \item Takes the \textbf{physical netlist} and maps the connections between BELs onto physical switchboxes.
    \end{itemize}

@@

\bibliographystyle{ieeetr}
\bibliography{references}

>>>>

\documentclass{article}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{graphicx}

@@

\section{Abbreviations}
\begin{itemize}[label={--}, left=0.25cm] % Adjust label and left indent as desired
    \item FPGA: Field Programmable Gate Array
    \item VLSI: Very Large Scale Integration
    \item EDA: Electronic Design Automation
    \item VHSIC: Very High Speed Integrated Circuits
    \item HDL: Hardware Description Language
    \item VHDL: VHSIC HDL
    \item HLS: High Level Synthesis
    \item PL-PS: Programmable Logic - Processing System
    \item EDIF: Electronic Design Interchange Format
    \item HPWL: Half Perimeter Wire Length
\end{itemize}

\section{Keywords}
\begin{itemize}
    \item FPGA, EDA, Synthesis, Placement, Routing, Parallel, Optimization
\end{itemize}

@@

    \item \textbf{Synthesis}
    \begin{itemize}[label={--}, left=0.25cm]
        \item Takes a design written in a high-level HDL like VHDL or Verilog and "synthesizes" a \textbf{logical netlist} out of it. 
        \item The logical netlist is usually generated as an EDIF, JSON, or a low-level Verilog file. 
        \item The netlist describes the necessary basic elements of logic (BELs) and the wired connections between them that are necessary to implement the design.
    \end{itemize}

    \item \textbf{Placement}
    \begin{itemize}[label={--}, left=0.25cm]
        \item Takes the \textbf{logical netlist} and produces a \textbf{physical netlist}.
        \item For each BEL in the netlist, assign the BEL to a Cell, Site, and Tile on the physical FPGA device.
        \item History of the landscape of placement algorithms:
    \end{itemize}

    \item \textbf{Routing}
    \begin{itemize}[label={--}, left=0.25cm]
        \item Takes the \textbf{physical netlist} and maps the connections between BELs onto wires, interconnects, and switchboxes on the FPGA.
        \begin{figure}
            \begin{center}
                \includegraphics[width=0.75\textwidth]{figures/kraftwerk2.png}
            \end{center}
            \caption{Landscape of VLSI placement techniques (Spindler) \cite{kraftwerk2} }
            \label{fig:}
        \end{figure}
        \begin{figure}
            \begin{center}
                \includegraphics[width=0.95\textwidth]{figures/ProCha.png}
            \end{center}
            \caption{Historical timeline of VLSI placement techniques (Markov) \cite{ProCha} }
            \label{fig:}
        \end{figure}
    \end{itemize}

@@

\newpage
\bibliographystyle{ieeetr}
\nocite{*}
\bibliography{
    references/surveys,
    references/fpga_placement,
    references/vlsi_placement,
}
